Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-13 shanghai.tex
Changed canonicity to functoriality, and made a home for the heart of the matter: boxproduct.

@@

\section{Canonicity}

We have already seen that the trace of Frobenius defines a canonical isomorphism 
$t_T : \GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
In this section we expand on the canonicity of this group isomorphism.

\begin{proposition}
The isomorphism $t_T : \GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
is a natural transformation between the following two contravariant functors 
from the category of algebraic tori over $K$ to the category of abelian groups: 
\begin{enumerate}
\item $T \mapsto \GCiso{\GN{T}}$
\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
\end{enumerate}
\end{proposition}

\Clifton{I think I can prove this proposition without too much difficulty.}
\begin{proof}
\end{proof}

>>>>

\section{Boxproduct}

Let $ \GC(G_1) \boxtimes \GC(G_2)$

\begin{proposition}\label{prop:product}
The rule ... defines an equivalence of categories 
\[
\GC(G_1\times G_2) \to \GC(G_1) \boxtimes \GC(G_2)
\]
and 
\[
\begin{tikzcd}
\GCiso{G_1\times G_2} \arrow{r} & \GCiso{G_1} \times \GCiso{G_2}\\
(G_1\times G_2)(k)^* \arrow{r}  & G_1(k)^* \times G_2(K)^*
\end{tikzcd}
\]
commutes.
\end{proposition}

@@

\section{Functoriality}

We have already seen that the trace of Frobenius defines a canonical homomorphism $\GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
In this section we show that this homomorphism is functorial, in the following sense.

\begin{proposition}
Trace of Frobenius $\GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
is a natural transformation between the following two additive functors from the additive category of algebraic tori over $K$ to the category of abelian groups: 
\begin{enumerate}
\item[$F_1$:] $T \mapsto \GCiso{\GN{T}}$;
\item[$F_2$:] $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
\end{enumerate}
\end{proposition}

\begin{proof}
When combined with the definition of $\GC(\GN{T})$ and Property~\ref{T(K)}, the first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$. When further combined with Proposition~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
\end{proof}
